\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[10pt,ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme[]{CambridgeUS}
\usecolortheme{dove}
\usefonttheme{structurebold}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Predicting crime rates using taxi rides in NYC},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\newif\ifbibliography
% Prevent slide breaks in the middle of a paragraph:
\widowpenalties 1 10000
\raggedbottom
\AtBeginPart{
  \let\insertpartnumber\relax
  \let\partname\relax
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \let\insertsectionnumber\relax
    \let\sectionname\relax
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \let\insertsubsectionnumber\relax
  \let\subsectionname\relax
  \frame{\subsectionpage}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\author{Carlos Petricioli \and
    Varsha Muralidharan   \and
    Valerie Angulo  }

\institute[New York University]{ New York University \\ \{cpa253,vm1370,vaa238\}@nyu.edu }

\setbeamerfont{headline}{size=\fontsize{8}{1}\selectfont}
\setbeamertemplate{headline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=1\paperwidth,ht=2.3ex,dp=1.5ex,right]{section in head/foot}%
    \usebeamerfont{section in head/foot}\insertsectionhead\hspace*{1ex}
  \end{beamercolorbox}%
  % \begin{beamercolorbox}[wd=0\paperwidth,ht=2.65ex,dp=1.5ex,right]{subsection in head/foot}%
  %   \usebeamerfont{subsection in head/foot}\hspace*{2ex}\insertsubsectionhead
  % \end{beamercolorbox}
  }%
  \vskip0pt%
}


% \setbeamertemplate{navigation symbols}{}
% \setbeamertemplate{footline}[page number]
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
      \begin{beamercolorbox}[wd=1\paperwidth,ht=2.25ex,dp=1ex,right]{author in head/foot}%
          \usebeamerfont{author in head/foot}
          \insertframenumber{} of  \inserttotalframenumber\hspace*{2ex} 
      \end{beamercolorbox}}%
      \vskip0pt%
}

% Set Color ==============================
% Custom colors
\usepackage{xcolor}

%\definecolor{gold}{HTML}{FDD017}
\definecolor{gold}{HTML}{fdde5c}
% \definecolor{deep sky blue}{HTML}{3BB9FF}
% \definecolor{light sky blue}{HTML}{82CAFA}

\makeatletter
\definecolor{mybackground}{HTML}{fef5d0}
\definecolor{myforeground}{HTML}{0000A0}

\setbeamercolor{normal text}{fg=black,bg=white}
\setbeamercolor{alerted text}{fg=red}
\setbeamercolor{example text}{fg=black}

\setbeamercolor{background canvas}{fg=myforeground, bg=white}
\setbeamercolor{background}{fg=myforeground, bg=mybackground}

\setbeamercolor{palette primary}{fg=black, bg=gray!30!white}
\setbeamercolor{palette secondary}{fg=black, bg=gray!20!white}
\setbeamercolor{palette tertiary}{fg=black, bg=gold}
\makeatother

\title{Predicting crime rates using taxi rides in NYC}
\date{12/15/2017}

\begin{document}
\frame{\titlepage}

\begin{frame}{%
\protect\hypertarget{big-data-analytics-symposium---fall-2017}{%
Big Data Analytics Symposium - Fall 2017}}

\begin{block}{Analytics Project}

Predicting crime rates using taxi rides in NYC

\end{block}

\begin{block}{Team}

\begin{itemize}
\item
  Carlos Petricioli (cpa253)
\item
  Varsha Muralidharan (vm1370)
\item
  Valerie Angulo (vaa238)
\end{itemize}

\end{block}

\begin{block}{Abstract}

\begin{itemize}
\tightlist
\item
  We study crime rates and its relationship on how people use of taxis
  in New York City.
\item
  Our hypothesis is that people are less likely to walk in areas
  subjectively deemed more dangerous and will instead opt to use more
  reliable and immediate transportation such as designated taxis.
\item
  WE FOUND THAT \_\_\_\_.
\end{itemize}

\end{block}

\end{frame}

\hypertarget{predicting-crime-rates-using-taxi-rides-in-nyc}{%
\section{Predicting crime rates using taxi rides in
NYC}\label{predicting-crime-rates-using-taxi-rides-in-nyc}}

\begin{frame}{%
\protect\hypertarget{motivation}{%
Motivation}}

\begin{block}{Who are the users of this analytic?}

\textless{} Short description of why this analytic is important
\textgreater{}

\end{block}

\begin{block}{who will benefit?}

BENEFIT

\end{block}

\begin{block}{Why is this analytic important?}

\textless{} Short description of why this analytic is important
\textgreater{}

\end{block}

\end{frame}

\begin{frame}{%
\protect\hypertarget{goodness}{%
Goodness}}

\begin{block}{cleaning data}

we made sure that –

\end{block}

\begin{block}{model testing}

we made sure that –

\end{block}

\end{frame}

\begin{frame}{%
\protect\hypertarget{data-sources}{%
Data Sources}}

Name: \textless{}Data Source 1 Name\textgreater{} Description:
\textless{}Brief description\ldots{}\textgreater{} Size of data:
\textless{}Size\ldots{}\textgreater{}

Name: \textless{}Data Source 2 Name\textgreater{} Description:
\textless{}Brief description\ldots{}\textgreater{} Size of data:
\textless{}Size\ldots{}\textgreater{} \ldots{} Name: Description:
\textless{}Brief description\ldots{}\textgreater{} Size of data:
\textless{}Size\ldots{}\textgreater{}

\end{frame}

\begin{frame}{%
\protect\hypertarget{design-diagram}{%
Design Diagram}}

\textless{} Insert one or more design diagrams here. Diagrams should
show inputs, outputs, tools used. \textgreater{}

Platform(s) on which the analytic ran: \textless{} Did you use the
Quickstart VM? NYU HPC cluster? Amazon AWS? Google GCE? Multiple
platforms? \textgreater{}

\end{frame}

\begin{frame}{%
\protect\hypertarget{results}{%
Results}}

\begin{enumerate}
[1.]
\item
  \textless{}Result 1\textgreater{} \textless{} Tell us a maximum of
  three results, insights, observations, or outcomes\ldots{}
  \textgreater{}
\item
  \textless{}Result 2\textgreater{}
\item
  \textless{}Result 3\textgreater{}
\end{enumerate}

\end{frame}

\begin{frame}{%
\protect\hypertarget{obstacles}{%
Obstacles}}

\begin{enumerate}
[1.]
\item
   \textless{} Tell us up to two obstacles you experienced in developing
  this analytic. \textgreater{}
\item
  \textless{}Obstacle 2\textgreater{}
\end{enumerate}

\end{frame}

\begin{frame}{%
\protect\hypertarget{summary}{%
Summary}}

\textless{}Brief wrap-up!\textgreater{}

\end{frame}

\begin{frame}{%
\protect\hypertarget{acknowledgements}{%
Acknowledgements}}

\textless{} If you used an Amazon AWS voucher for this work, thank
Amazon here. If you had help from HPC, thank them for their support
here. If you received data from some source that was kind enough to
share their data with you, thank them here. If you worked with a domain
expert, you know what to do\ldots{} \textgreater{}

\end{frame}

\begin{frame}{%
\protect\hypertarget{references}{%
References}}

\textless{} List the work you referenced \textgreater{}

\end{frame}

\hypertarget{thank-you}{%
\section{Thank you!}\label{thank-you}}

\end{document}
